A quadratic-time algorithm for the cardinality-constrained college application problem

### 2022-07-14 paper_alma/body.tex
refactor paper_alma to match paper_ellis, expand introduction

%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article} %try amsproc, amsart
\usepackage{geometry}       \geometry{a4paper, margin=2.5cm}
\usepackage{setspace}       \setstretch{1.1}
\usepackage{hyperref}       \hyperbaseurl{}    
                            \urlstyle{same}
\usepackage[ruled,linesnumbered]{algorithm2e}   \SetKwInOut{KwParams}{Parameters}
                                                \newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}
\usepackage{stackengine}    \newcommand\xrowht[2][0]{\addstackgap[.5\dimexpr#2\relax]{\vphantom{#1}}}
\usepackage[style=numeric]{biblatex}
\addbibresource{refs.bib}

% Author block
\usepackage{authblk}

\title{A quadratic-time algorithm for the cardinality-constrained college application problem}
\author[1]{Max Kapur}
\author[2]{Sung-Pil Hong}
\affil[1,2]{Department of Industrial Engineering, Seoul National University}
\date{\today}

% Math
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}

%\numberwithin{equation}{section}
%\numberwithin{theorem}{section}
%\numberwithin{lemma}{section}
%\numberwithin{corollary}{section}
%\numberwithin{proposition}{section}
%\numberwithin{example}{section}
%\numberwithin{definition}{section}
%\numberwithin{problem}{section}
%\numberwithin{assumption}{section}
%\numberwithin{conjecture}{section}

\begin{document}

\maketitle

\begin{abstract}
%\input{abstract.tex}
This paper considers a novel portfolio optimization problem called the college application problem. We show that the objective function is a nondecreasing submodular set function and provide a quadratic-time solution algorithm. We discuss the properties of the optimal solution and their implications for student welfare.

\textbf{Keywords:} combinatorial optimization, submodular maximization, portfolio optimization

\vfill
Correspondence may be addressed to Max Kapur.
\begin{itemize}
%\item[] Correspondence may be addressed to Max Kapur.

\item[] Email: \url{maxkapur@gmail.com}

\item[] Address: 39-411, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea
\end{itemize}

\end{abstract}

\pagebreak

\tableofcontents

%\input{body.tex}

@@

Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.

Most quantitative research on college admissions to date has been descriptive in nature. A standard benchmark for logistic regression techniques, for example, involves estimating students' admissions probabilities from information about their past academic performance (Acharya et al. 2019; Lim 2013). When professional admissions consultants advise their clients on where to apply to college, however, they but typically rely on qualitative heuristics, such as balancing applications between safety and reach schools, rather than optimization models (Peck 2021). (Admissions consultants refer to schools with low utility and high admissions probability as \emph{safety schools}, and those with high utility and low admissions probability as \emph{reach schools.})

In the present study, we formulate the student's college application decision as the following optimization problem:
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~|\mathcal{X}| \leq H
\end{split}
\end{align}
Here $\mathcal{C} = \{ 1 \dots m\}$ is an index set; $h > 0$ is the number of students the student can apply to; for $j = 1 \dots m$, $Z_j$ is a random, independent Bernoulli variable with probability $f_j$; and for $j = 0\dots m$, $t_j\geq 0$ is a utility parameter.

Consider a single prospective student in a college market with $m$ colleges, and let each $t_j$-value indicate the utility she associates with attending school $j$, where her utility is $t_0$ if she does not attend college. Let $h$ denote the number of schools to which the student can afford to apply. Lastly, let $f_j$ denote the student's probability of being admitted to school $j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she is admitted to. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.

% def greedy, nested
We focus on the special case in which students are constrained in the \emph{number} of schools to which they can apply, and show that the optimal portfolios in this case are nested in the budget constraint, implying the optimality of the greedy algorithm that adds schools one at a time according to how much they increase the objective value.

@@

The objective function is a monotonic submodular function in the sense first described by Nemhauser et al. (1978). They showed that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for optimizing a monotonic submodular function over a cardinality constraint, and a subsequent result of Nemhauser and Wolsey (1978) proved that this approximation ratio is the best achievable by a polynomial-time algorithm. In the special case of college application, however, we show that the same algorithm is exact.

% define nestedness
The proof of the optimality of the greedy algorithm rests on the nested structure of the portfolios, a property that is of independent interest. As Rozanov and Tamir (2020) articulate, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges reward students who tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the optimal portfolio.
% Greedy algorithms produce a \emph{nested} family of solutions parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$.

Fu (2014) considered a problem that is reducible to ours: since application is at cost rather than a constraint, the objective function is separable in the cost and therefore must be optimal over portfolios of the given size. Thus, solving her problem reduces to solving $m$ instances of \eqref{headlineproblem}.

@@

To the best of our knowledge, the first systematic study of the college application problem was undertaken by Kapur in his master's thesis, which considers \eqref{headlineproblem} as well as the more general case of a knapsack constraint. The present study extends Kapur's results with a further discussion of the application strategies recommended in the admissions consulting industry and how these compare to the optimal strategy.

@@

\begin{proof}
It is self-evident that $v(\mathcal{X})$ is nondecreasing. To establish its submodularity, we apply proposition 2.1.iii of Nemhauser and Wolsey (1978) and show that
\begin{equation}\label{nemhauseriii}
v(\mathcal{X} \cup \{j\}) - v(\mathcal{X}) \geq 
v(\mathcal{X} \cup \{j, k\}) - v(\mathcal{X} \cup \{k\})
\end{equation}
for $\mathcal{X} \subset \mathcal{C}$ and $j \neq k \in \mathcal{C} \setminus \mathcal{X}$. By Lemma \ref{eliminationtheorem}, we can repeatedly eliminate the schools in $\mathcal{X}$ according to \eqref{howtotransformtj} to obtain a portfolio valuation function $w(\mathcal{Y})$ with parameter $\bar t$ such that $w(\mathcal{Y}) = v(\mathcal{X} \cup \mathcal{Y}) + \text{const.}$ for any $\mathcal{Y} \subseteq \mathcal{C} \setminus \mathcal{X}$. Therefore, \eqref{nemhauseriii} is equivalent to
\begin{align}
& w(\{j\}) - w(\varnothing) \geq w(\{j, k\}) - w(\{k\}) \\
\iff \qquad &w(\{j\})  +  w(\{k\})  \geq w(\{j, k\})  \\
\iff \qquad &\operatorname{E}[\,\bar t_j Z_j\,] + \operatorname{E}[\,\bar t_k Z_k\,] 
\geq \operatorname{E}\bigl[\max\{ \bar t_j Z_j, \bar t_k Z_k \} \bigr]
\end{align}
which is plainly true. 
\end{proof}

@@

In real-world admissions markets, $f_t$ and $t_j$ correlate inversely because desirable schools attract many applicants. In the admissions consulting industry, schools with high utility and low admissions probability are called reach schools, while schools with low utility and high admissions probability are called safety schools, and those in between are called target schools. According to a common heuristic used by admissions consultants, it is best to apply to a roughly equal mix of target, safety, and reach schools (Jeon 2015, Peck 2021). How does this strategy, which we call the \emph{distributional} heuristic, perform compared to the optimal application strategy?

@@

The expected utility associated with applying to school $j$ alone is is simply $\operatorname{E}[t_j Z_j] = f_j t_j$. It is therefore tempting to adopt the following heuristic:
\begin{definition}[Linearization heuristic for the college application problem] \label{naivealgorithm}
Apply to the $h$ schools having the highest expected utility $f_j t_j$.
\end{definition}
\noindent This algorithm's computation time is $O(m)$ using the PICK algorithm of Blum et al. (1973). In essence, this heuristic maximizes $\operatorname{E}\left[\,\sum t_j Z_j\, \right]$ as a surrogate for the true objective function $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. Accordingly, we call it the \emph{linearization heuristic.}

@@

\noindent (An elementary proof appears in Kapur (2022).) It follows that when $\mathcal{X}_h$ is the optimal $h$-portfolio for a given market, $v(\mathcal{X}_h)$ is $O(h)$. Example \ref{tightexampleforoneoverhopt}, in which $v(\mathcal{X}_h)$ can be made arbitrarily close to $h$, establishes the tightness of this bound.

@@

\section{References}

%\printbibliography

\parskip 0em
\leftskip 2em
\parindent -2em

\indent\indent Acharya, Mohan S., Asfia Armaan, and Aneeta S. Antony. 2019. ``A Comparison of Regression Models for Prediction of Graduate Admissions.'' In \emph{Second International Conference on Computational Intelligence in Data Science.} \url{https://doi.org/10.1109/ICCIDS.2019.8862140}.

Ashlagi, Itai, and Afshin Nikzad. 2020. ``What Matters in School Choice Tie-Breaking? How Competition Guides Design.'' \emph{Journal of Economic Theory} 190: article no. 105120. \url{https://doi.org/10.1016/j.jet.2020.105120}.

Assad, Arjang. 1985. ``Nested Optimal Policies for Set Functions with Applications to Scheduling.'' \emph{Mathematics of Operations Research} 10 (1): 82--99.

Azevedo, Eduardo and Jacob Leshno. 2016. ``A Supply and Demand Framework for Two-Sided Matching Markets.'' \emph{Journal of Political Economy} 124 (5): 1235--68. \url{https://doi.org/10.1086/687476}.

Badanidiyuru, Ashwinkumar and Jan Vondrák. 2014. ``Fast Algorithms for Maximizing Submodular Functions.'' In \emph{Proceedings of the 2014 Annual ACM--SIAM Symposium on Discrete Algorithms}, 1497--1514. \url{https://doi.org/10.1137/1.9781611973402.110}.

Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B. Shah. 2017. ``Julia: A Fresh Approach to Numerical Computing.'' \emph{SIAM Review} 59: 65–98. \url{https://doi.org/10.1137/141000671}.

Blum,  Manuel, Robert W. Floyd, Vaughan Pratt, Ronald L. Rivest, and Robert E. Tarjan. 1973. ``Time Bounds for Selection.'' \emph{Journal of Computer and System Sciences} 7 (4): 448--61. \url{https://doi.org/10.1016/S0022-0000(73)80033-9}.

Bodoh-Creed, Aaron. 2020. ``Optimizing for Distributional Goals in School Choice Problems.'' \emph{Management Science} 66 (8): 3657--76. \url{https://doi.org/10.1287/mnsc.2019.3376}.

%Budish, Eric. 2011. ``The Combinatorial Assignment Problem: Approximate Competitive Equilibrium from Equal Incomes.'' \emph{Journal of Political Economy} 119 (6): 1061--1103. \url{https://doi.org/10.1086/664613}.

% 1 - 1/e opt for the problem in the title
Calinescu, Gruia, Chandra Chekuri, Martin Pál, and Jan Vondrák. 2011. ``Maximizing a Monotone Submodular Function Subject to a Matroid Constraint.'' \emph{SIAM Journal on Computing} 40 (6): 1740--66. \url{https://doi.org/10.1137/080733991}.

Carraway, Robert, Robert Schmidt, and Lawrence Weatherford. 1993. ``An Algorithm for Maximizing Target Achievement in the Stochastic Knapsack Problem with Normal Returns.'' \emph{Naval Research Logistics} 40 (2): 161--73. \url{https://doi.org/10.1002/nav.3220400203}.

Chekuri, Chandra, Jan Vondr\'ak, and Rico Zenklusen. 2014. ``Submodular Function Maximization via the Multilinear Relaxation and Contention Resolution Schemes.'' \emph{SIAM Journal on Computing} 43 (6): 1831--79. \url{https://doi.org/10.1137/110839655}.

Cormen, Thomas, Charles Leiserson, and Ronald Rivest. 1990. \emph{Introduction to Algorithms.} Cambridge, MA: The MIT Press.

Dantzig, George B. 1957. ``Discrete-Variable Extremum Problems.'' \emph{Operations Research} 5 (2): 266--88.

Dean, Brian, Michel Goemans, and Jan Vondr\'ak. 2008. ``Approximating the Stochastic Knapsack Problem: The Benefit of Adaptivity.'' \emph{Mathematics of Operations Research} 33 (4): 945--64. \url{https://doi.org/10.1287/moor.1080.0330}.

Edmonds, Jack. 1971. ``Matroids and the Greedy Algorithm.'' \emph{Mathematical Programming} 1: 127--36. \url{https://doi.org/10.1007/BF01584082}.

%Fredman, Michael Lawrence and Robert Tarjan. 1987. ``Fibonacci Heaps and Their Uses in Improved Network Optimization Algorithms.'' \emph{Journal of the Association for Computing Machinery} 34 (3): 596--615.

Fu, Chao. 2014. ``Equilibrium Tuition, Applications, Admissions, and Enrollment in the College Market.'' \emph{Journal of Political Economy} 122 (2): 225--81. \url{https://doi.org/10.1086/675503}.

Gale, David, and Lloyd Shapley. 1962. ``College Admissions and the Stability of Marriage.'' \emph{American Mathematics Monthly} 69 (1): 9--15. \url{https://doi.org/10.2307/2312726}.

Garey, Michael and David Johnson. 1979. \emph{Computers and Intractability: A Guide to the Theory of NP-Completeness.} New York: W. H. Freeman and Company.

Hartlaub, Vanessa and Thorsten Schneider. 2012. “Educational Choice and Risk Aversion: How Important Is Structural vs. Individual Risk Aversion?” \emph{SOEPpapers on Multidisciplinary Panel Data Research,} no. 433. \url{https://www.diw.de/documents/publikationen/73/diw_01.c.394455.de/diw_sp0433.pdf}.

Jeon, Minhee. 2015. ``[College application strategy] Six chances total\dots divide applications across reach, target, and safety schools'' (in Korean). Jungang Ilbo, Aug. 26. \url{https://www.joongang.co.kr/article/18524069}.

Kahneman, Daniel. 2011. \emph{Thinking, Fast and Slow.} New York: Macmillan.

Kapur, Max. 2021. ``Characterizing Nonatomic Admissions Markets.'' ArXiv, July 3, 2021. \url{https://arxiv.org/abs/2107.01340}.

Kellerer, Hans, Ulrich Pferschy, and David Pisinger. 2004. \emph{Knapsack Problems.} Berlin: Springer.

%1 - 1/ e for monotonic submodular with knapsack constraints, i.e. Ellis with 가나다
Kulik, Ariel, Hadas Shachnai, and Tami Tamir. 2013. ``Approximations for Monotone and Nonmonotone Submodular Maximization with Knapsack Constraints.'' \emph{Mathematics of Operations Research} 38 (4): 729--39. \url{https://doi.org/10.1287/moor.2013.0592}.

Lim, Daniel Kibum. 2013. ``A Simulation Approach to Predicting College Admissions.'' Master's thesis, University of California Los Angeles. \url{https://escholarship.org/uc/item/8r2695n5}.

Markowitz, Harry. 1952. ``Portfolio Selection.'' \emph{The Journal of Finance} 7 (1): 77--91. \url{https://www.jstor.org/stable/2975974}.

Martello, Silvano and Paolo Toth. 1990. \emph{Knapsack Problems: Algorithms and Computer Implementations.} New York: John Wiley \& Sons.

Meucci, Attilio. 2005. \emph{Risk and Asset Allocation.} Berlin: Springer-Verlag, 2005.

% 1 - 1/e inapproximability of submodular maximization
Nemhauser, George and Laurence Wolsey. 1978. ``Best Algorithms for Approximating the Maximum of a Submodular Set Function.'' \emph{Mathematics of Operations Research} 3 (3): 177--88. \url{https://doi.org/10.1287/moor.3.3.177}.

Nemhauser, George, Laurence Wolsey, and Marshall Fisher. 1978. ``An Analysis of Approximations for Maximizing Submodular Set Functions—I.'' \emph{Mathematical Programming} 14: 265--94.

%Othman, Abraham, Eric Budish, and Tuomas Sandholm. 2010. ``Finding Approximate Competitive Equilibria: Efficient and Fair Course Allocation.'' In \emph{Proceedings of 9th International Conference on Autonomous Agents and Multiagent Systems.} New York: ACM. \url{https://dl.acm.org/doi/abs/10.5555/1838206.1838323}.

Parker, R. Gary and Ronald L. Rardin. 1988. \emph{Discrete Optimization.} San Diego: Academic Press.

Roth, Alvin E. 1982. ``The Economics of Matching: Stability and Incentives.'' \emph{Mathematics of Operations Research} 7 (4): 617--28. \url{https://www.jstor.org/stable/3689483}.

Rozanov, Mark and Arie Tamir. 2020. ``The Nestedness Property of the Convex Ordered Median Location Problem on a Tree.'' \emph{Discrete Optimization} 36: 100581. \url{https://doi.org/10.1016/j.disopt.2020.100581}.

Sklarow, Mark. 2018. \emph{State of the Profession 2018: The 10 Trends Reshaping Independent Educational Consulting.} Technical report, Independent Educational Consultants Association. \url{https://www.iecaonline.com/wp-content/uploads/2020/02/IECA-Current-Trends-2018.pdf}.

Sniedovich, Moshe. 1980. ``Preference Order Stochastic Knapsack Problems: Methodological Issues.'' \emph{The Journal of the Operational Research Society} 31 (11): 1025--32. \url{https://www.jstor.org/stable/2581283}.

Steinberg, E. and M. S. Parks. 1979. ``A Preference Order Dynamic Program for a Knapsack Problem with Stochastic Rewards.'' \emph{The Journal of the Operational Research Society} 30 (2): 141--47. \url{https://www.jstor.org/stable/3009295}.

% Another ex of nestedness.
%Tibshirani, Robert. 1996. ``Regression Shrinkage and Selection via the Lasso.'' \emph{Journal of the Royal Statistical Society,. Series B (Methodological)} 58, no. 1: 267--88. \url{https://www.jstor.org/stable/2346178}.

Van Huizen, Thomas and Rob Alessie. 2019. ``Risk Aversion and Job Mobility.’’ \emph{Journal of Economic Behavior \& Organization} 164: 91--106. \url{https://doi.org/10.1016/j.jebo.2019.01.021}.

Vazirani, Vijay. 2001. \emph{Approximation Algorithms.} Berlin: Springer.

Wolsey, Laurence. 1998. \emph{Integer Programming.} New York: John Wiley \& Sons.

\end{document}

\ifen \section{Introduction}  \else \section{서론} \fi
\ifen This paper considers the following optimization problem:
\else 본 논문은 다음과 같은 최적화 문제를 고려한다.\fi
%\begin{definition}[Optimal college application portfolio] \label{generalproblemstatement}
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~\sum_{j\in \mathcal{X}} g_j \leq H
\end{split}
\end{align}
%\end{definition}
\ifen Here $\mathcal{C} = \{ 1 \dots m\}$ is an index set; $H > 0$ is a budget parameter; for $j = 1 \dots m$, $g_j > 0$ is a cost parameter and $Z_j$ is a random, independent Bernoulli variable with probability $f_j$; and for $j = 0\dots m$, $t_j\geq 0$ is a utility parameter. 
\else 단,  $\mathcal{C} = \{ 1 \dots m\}$은 지표 집합이며 $H$는 예산을 나타내는 모수다. 각 $j = 1 \dots m$에 대해 $g_j > 0$는 비용 모수이며 $Z_j$는 확률 $f_j$를 가지는 서로 독립적인 Bernoulli 변수다. 각 $j = 0 \dots m$에 대해 $t_j\geq 0$는 효용 모수다. \fi

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she is admitted to. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. 
\else
다음 해석에 따라 이를 `대학 입학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최댓값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다.
\fi

\ifen
The college application problem is not solely of theoretical interest. Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy. However, while predicting admissions outcomes on a school-by-school basis is a standard benchmark for logistic regression models (Acharya et al. 2019; Lim 2013), we believe our study is the first to focus on the overall application strategy as an optimization problem.

The problem is also conformable to other competitive matching games such as job application. Here, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.
\else
대학 입학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 급료는 평균 200달러다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용하여 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 로지스틱 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019; Lim 2013)지만, 전체적인 지원 전략에 집중하여 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.

취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위의 문제를 적용할 수 있다. 이때, 예산 제약 조건은 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수 있다.
\fi

>>>>

@@

Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools \cite{sklarow2018}. In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.

Most quantitative research on college admissions to date has been descriptive in nature. A standard benchmark for logistic regression techniques, for example, involves estimating students' admissions probabilities from information about their past academic performance \cite{acharyaetal2019,lim2013}. When professional admissions consultants advise their clients on where to apply to college, however, they typically rely on qualitative heuristics, such as balancing applications between safety and reach schools, rather than optimization models \cite{jeon2015,peck2021}. (Admissions consultants refer to schools with low utility and high admissions probability as \emph{safety schools}, and those with high utility and low admissions probability as \emph{reach schools.})

In the present study, we formulate the student's college application decision as the following combinatorial optimization problem:
\begin{align} \label{headlineproblem}
\begin{split}
\text{maximize}\quad & v(\mathcal{X}) =  \operatorname{E}\Bigl[\max\bigr\{t_0,
\max\{t_j Z_j : j \in \mathcal{X}\}\bigr\}\Bigr] \\
\text{subject to}\quad & \mathcal{X} \subseteq \mathcal{C}, ~~|\mathcal{X}| \leq H
\end{split}
\end{align}
Here $\mathcal{C} = \{ 1 \dots m\}$ represents the set of colleges in the market and $h > 0$ is the number of colleges the student can apply to. For $j = 1 \dots m$, let $f_j$ denote the student's probability of being admitted to school $j$ if she applies and $Z_j$ a random, independent Bernoulli variable with probability $f_j$, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). For $j = 0\dots m$, $t_j\geq 0$ indicates the utility she associates with attending school $j$, where her utility is $t_0$ if she does not attend college. Then the student's objective is to maximize the expected utility associated with the best school she is admitted to. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies, which we call her application \emph{portfolio.}

The problem can also be applied to other competitive matching games such as job application and marriage proposals. Here the budget constraint may arise due to the time required to communicate with each applicant or a legal limit on the number of applications allowed.

We show that the optimal portfolios for the cardinality-constrained college are \emph{nested} in the budget constraint, meaning that where $\mathcal{X}_h$ denotes the optimal portfolio for budget $h$, $\mathcal{X}_h \subset \mathcal{X}_{h+1}$. The nestedness property is equivalent to the optimality of the \emph{greedy} algorithm that iteratively adds to $\mathcal{X}$ the school that elicits the greatest increase in the objective value. The proof of the nestedness property yields insight into the properties of the optimal college application strategy: Students who cannot afford to apply to many schools allocate a greater proportion of their application budget to safety schools than students with a large application budget. A classic finding of behavioral psychology is that agents with limited resources tend to make more risk-averse decisions than their wealthier peers, especially with respect to education and career choice \cite{hartlaubandschneider2012,vanhuizenandalessie2019}. In the case of college application, our model provides a rational basis for this tendency. % cite

Our analysis of the college application problem also yields tight bounds on the marginal value of an additional application, which may be useful in designing admissions markets. % i.e. in Korea the limit is 3; therefore we know that adding an additional school would yield at the very most a 33 pct increase in student welfare

@@

The objective function is a monotonic submodular function in the sense first described by Nemhauser et al. \cite{nemhauseretal1978}. They showed that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for optimizing a monotonic submodular function over a cardinality constraint, and a subsequent result of Nemhauser and Wolsey \cite{nemhauserandwolsey1978} proved that this approximation ratio is the best achievable by a polynomial-time algorithm. In the special case of college application, however, we show that the same algorithm is exact.

% define nestedness
The proof of the optimality of the greedy algorithm rests on the nested structure of the portfolios, a property that is of independent interest. As Rozanov and Tamir \cite{rozanovandtamir2020} articulate, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges reward students who tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the optimal portfolio.
% Greedy algorithms produce a \emph{nested} family of solutions parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$.

Fu \cite{fu2014} considered a problem that is reducible to ours: since application is at cost rather than a constraint, the objective function is separable in the cost and therefore must be optimal over portfolios of the given size. Thus, solving her problem reduces to solving $m$ instances of \eqref{headlineproblem}.

@@

To the best of our knowledge, the first systematic study of the college application problem was undertaken by Kapur in his master's thesis \cite{kapur2022}, which considers \eqref{headlineproblem} as well as the more general case of a knapsack constraint. The present study extends Kapur's results with a further discussion of the application strategies recommended in the admissions consulting industry and how these compare to the optimal strategy.

@@

\begin{proof}
It is self-evident that $v(\mathcal{X})$ is nondecreasing. To establish its submodularity, we apply proposition 2.1.iii of \cite{nemhauserandwolsey1978} and show that
\begin{equation}\label{nemhauseriii}
v(\mathcal{X} \cup \{j\}) - v(\mathcal{X}) \geq 
v(\mathcal{X} \cup \{j, k\}) - v(\mathcal{X} \cup \{k\})
\end{equation}
for $\mathcal{X} \subset \mathcal{C}$ and $j \neq k \in \mathcal{C} \setminus \mathcal{X}$. By Lemma \ref{eliminationtheorem}, we can repeatedly eliminate the schools in $\mathcal{X}$ according to \eqref{howtotransformtj} to obtain a portfolio valuation function $w(\mathcal{Y})$ with parameter $\bar t$ such that $w(\mathcal{Y}) = v(\mathcal{X} \cup \mathcal{Y}) + \text{const.}$ for any $\mathcal{Y} \subseteq \mathcal{C} \setminus \mathcal{X}$. Therefore, \eqref{nemhauseriii} is equivalent to
\begin{align}
& w(\{j\}) - w(\varnothing) \geq w(\{j, k\}) - w(\{k\}) \\
\iff \qquad &w(\{j\})  +  w(\{k\})  \geq w(\{j, k\})  \\
\iff \qquad &\operatorname{E}[\,\bar t_j Z_j\,] + \operatorname{E}[\,\bar t_k Z_k\,] 
\geq \operatorname{E}\bigl[\max\{ \bar t_j Z_j, \bar t_k Z_k \} \bigr]
\end{align}
which is plainly true. 
\end{proof}

@@

In real-world admissions markets, $f_t$ and $t_j$ correlate inversely because desirable schools attract many applicants. In the admissions consulting industry, schools with high utility and low admissions probability are called reach schools, while schools with low utility and high admissions probability are called safety schools, and those in between are called target schools. According to a common heuristic used by admissions consultants, it is best to apply to a roughly equal mix of target, safety, and reach schools \cite{jeon2015,peck2021}. How does this strategy, which we call the \emph{distributional} heuristic, perform compared to the optimal application strategy?

@@

The expected utility associated with applying to school $j$ alone is is simply $\operatorname{E}[t_j Z_j] = f_j t_j$. It is therefore tempting to adopt the following heuristic:
\begin{definition}[Linearization heuristic for the college application problem] \label{naivealgorithm}
Apply to the $h$ schools having the highest expected utility $f_j t_j$.
\end{definition}
\noindent This algorithm's computation time is $O(m)$ using the PICK algorithm of \cite{blumetal1973}. In essence, this heuristic maximizes $\operatorname{E}\left[\,\sum t_j Z_j\, \right]$ as a surrogate for the true objective function $\operatorname{E}\left[\max \{t_j Z_j\} \right]$. Accordingly, we call it the \emph{linearization heuristic.}

@@

\noindent (An elementary proof is provided in \cite{kapur2022}.) It follows that when $\mathcal{X}_h$ is the optimal $h$-portfolio for a given market, $v(\mathcal{X}_h)$ is $O(h)$. Example \ref{tightexampleforoneoverhopt}, in which $v(\mathcal{X}_h)$ can be made arbitrarily close to $h$, establishes the tightness of this bound.

@@
